Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-05-14 ebayes_rnaseq_heterosis.tex
remove sec

\subsection{Implementation in \Stan{}}

@@

The supplementary materials include the maize experiment data ({\tt data.csv}), a script to run our method ({\tt script.R}), and the {\tt Stan} models: the all-genes-independent (\verb@model_ind.txt@) and covariance (\verb@model_cov.txt@) models used in obtaining MAP estimates, along with the single-gene-independent (\verb@sg_model_ind.txt@) and covariance (\verb@sg_model_cov.txt@) models used in performing the MCMC on single genes.

@@

% From Dan, "There are some capitalization issues in the references section.  I think you need to protect "RNA" with curly braces so that it stays capitalized.  Also, in Hallauer et al. (2010), the last initial should presumably be "D." rather than "d."."

>>>>

% \subsection{Implementation in \Stan{}}

@@

The supplementary materials include the maize experiment data ({\tt data.csv}), a script to run our method ({\tt script.R}), and the {\tt Stan} model (\verb@sg_model_ind.txt@).  
%the all-genes-independent (\verb@model_ind.txt@) and covariance (\verb@model_cov.txt@) models used in obtaining MAP estimates, along with the single-gene-independent (\verb@sg_model_ind.txt@) and covariance (\verb@sg_model_cov.txt@) models used in performing the MCMC on single genes.

@@
